A thesis draft

### 2018-09-17 draft.tex
Add content about docker

As already introduced before, Kubernetes is an open source software framework 
specialized in container management and orchestration. Developed by Google in 
??\todo{Find out the actual date} and written in Go, it allows different 
machines (called nodes from now on) to create an abstraction layer and to form a 
cluster where is possible to run Docker containers without brothering about 
hardware constraints. Nodes can have specific roles and specialization, all of 
them managed by one or many master nodes, that actually manage the 
orchestration.
On top of that, Kubernetes astrae from the virtualization in-use, giving the 
possibility to change the virtualization software in use (i.e. from 
Container-based technology to Virtual machine software).

>>>>

As already introduced before, Kubernetes is an open source software framework 
specialized in container management and orchestration. Developed by Google in 
??\todo{Find out the actual date} and written in Go, it allows different 
machines (called nodes from now on) to create an abstraction layer and to form a 
cluster where is possible to run Docker containers without brothering about 
hardware constraints. Nodes can have specific roles and specialization, all of 
them managed by one or many master nodes, that actually manage the 
orchestration.
On top of that, Kubernetes is virtualization-agnostic, meaning that it offers 
the possibility to change the virtualization software in use (i.e. from 
Container-based technology to Virtual machine software).

\subsubsection{About Docker}

In recent years, with the new hardware capabilities and the recent development 
of in-kernel virtualization systems (such as Hyper-V) this technology 
begin to be adopted. Virtualization allows to run different systems on the 
same machine, making them completely isolated and then more resilient to 
failure. The back of the medal, though, is that virtual machines requires large 
amount of resources, especially memory, because solutions like copy-and-write 
of in-memory pages are not viable anymore, leading to duplication of loaded 
libraries and assets in the memory of the host. For large deployment containing 
only simple services (e.g. a backend application serving a website or a 
database) this result in a waste of resources. \todo{Talk about lxc containers 
and how Docker solved magically the problem.}

, finally leading to , especially 
regarding memory consumption.
